Resiliencia de *Quercus pyrenaica* a dos eventos de sequía

### 2017-12-12 pres/state_ms.Rmd
update state

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r, echo=FALSE}
library(knitr)
df <- read.csv(file='../out/anovas_resilience/huber_evi/trimmed_anovas.csv', header=TRUE)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
```

@@

```{r, echo=FALSE}
df <- read.csv(here("/out/anovas_resilience/huber_evi", "trimmed_anovas.csv"), header = TRUE)
names(df) <- c('factores', 'F', 'p', 'variables')

dff <- df %>% gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Disturb", 
                           "disturb_year:site" = "Disturb X Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Disturb", "Site", "Disturb X Site")))

kable(dff, format = "latex", booktabs = T,
      col.names = c("", "F", "p", "F", "p", "F", "p", "F", "p"),
      digits=c(0,2,3,2,3,2,3,2,3)) %>% 
  kable_styling(font_size = 8) %>% 
  add_header_above(c("", "rc" = 2, "rrs" = 2, "rs" = 2, "rt" = 2))

# pandoc.table(dff,
#              round=c(0,2,3,2,3,2,3,2,3),
#              digits=c(0,5,4,5,4,5,4,5,4)
#              )
```
